Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-04-24 WorkSpace/Paper/Paper.tex
finished most of methods, namely prng descriptions and fixed author formatting to correctly represent ranking as per the template

\author{
\IEEEauthorblockN{Najib Ali}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{Matthew Hawks}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
\and
\IEEEauthorblockN{Jacob Anderson}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{Ryan Hines}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
\and
\IEEEauthorblockN{Spencer Arnold}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{Tae Kweon}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
}

@@

Below are short descriptions of each PRNG and any implementation notes made during the developement process.
Middle Square:
Description:
...
Notes:
A note on weakness: For a generator of n-digit numbers, the period can be no longer than 8n. If the middle n digits are all zeroes, 
the generator then outputs zeroes forever. If the first half of a number in the sequence is zeroes, the subsequent
numbers will be decreasing to zero. While these runs of zero are easy to detect, they occur too frequently for this
method to be of practical use. The middle-squared method can also get stuck on a number other than zero.

An already seen list is NOT included in the original middle square method and will not be used.

Linear Congruential:
Description:
...
Notes:
The generator is not sensitive to the choice of c, 
as long as it is relatively prime to the modulus 
(e.g. if m is a power of 2, then c must be odd), 
so the value c=1 is commonly chosen.

If c = 0, the generator is often called a multiplicative
congruential generator (MCG), or Lehmer RNG. If c ≠ 0, the
method is called a mixed congruential generator.

Parameters were chosen based on $2^32$ in table 2 of 
\url{https://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=BBA0C7ED3ADAB606642BB8D939774B4F?doi=10.1.1.34.1024&rep=rep1&type=pdf}

Lagged Fibonacci:
Description:
...
Notes:
This is two tap, not three tap...
It's a "lagged" generator, because "j" and "k" lag behind the generated pseudorandom value. 
Also, this is called a "two-tap" generator, in that you are using 2 values in the sequence 
to generate the pseudorandom number. However, a two-tap generator has some problems with 
randomness tests, such as the Birthday Spacings. Apparently, creating a "three-tap" generator
addresses this problem.

Park Miller:
Description:
...
Notes:
The Lehmer generator is an lcg. Park Miller is a specific lcg.

The Lehmer random number generator (named after D. H. Lehmer), 
sometimes also referred to as the Park–Miller random number generator
(after Stephen K. Park and Keith W. Miller), is a type of linear congruential generator (LCG).

Park miller generator, because they essentially the same.
Park-miller request the use of certain modulos.
Lehmer is an lcg where c = 0...
If c = 0, the generator is often called a multiplicative congruential generator (MCG),
or Lehmer RNG. If c ≠ 0, the method is called a mixed congruential generator.

While the Lehmer RNG can be viewed as a particular case of the linear congruential generator
with c=0, it is a special case that implies certain restrictions and properties.
In particular, for the Lehmer RNG, the initial seed must be coprime to the modulus m that is
not required for LCGs in general.

The choice of the modulus m and the multiplier a is also more restrictive for the Lehmer RNG.
In contrast to LCG, the maximum period of the Lehmer RNG equals m−1 and it is such when m is 
prime and a is a primitive root modulo m.

Mersenne Twister:
Description:
...
Notes:
Closely related with LFSRs. In its MT19937 implementation is probably the most commonly used modern PRNG. 
Default generator in the Python language starting from version 2.3.

We used numpy's version of the Mersenne Twister.

@@

Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively. The stack of convolutional layers allow the network to discover complex patterns in the input." [https://arxiv.org/pdf/1810.00378.pdf] Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus. Talk about the input xdata and ydata shape and reference the granular model Figure ~\ref{fig:Granular Experimental Model} for detail on how these data are aggregated.

>>>>

\author{
\IEEEauthorblockN{1\textsuperscript{st} Spencer Arnold}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{4\textsuperscript{th} Matthew Hawks}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Najib Ali}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{5\textsuperscript{th} Ryan Hines}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Jacob Anderson}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}\\[0.4cm]  %<------- Extra vertical space
\IEEEauthorblockN{6\textsuperscript{th} Tae Kweon}
\IEEEauthorblockA{\textit{Department of Computer Science}\\
\textit{Middle Tennessee State University}\\
Murfreesboro, Tennessee \\
email address}
}

@@

Below are short descriptions and non-inclusive general notes of each PRNG and any implementation notes made during the developement process.

\noindent\textbf{Middle Square}:
\begin{itemize}
    \item "To generate a sequence of n-digit pseudorandom numbers, an n-digit starting value is created and squared, producing a 2n-digit number. If the result has fewer than 2n digits, leading zeroes are added to compensate. The middle n digits of the result would be the next number in the sequence, and returned as the result. This process is then repeated to generate more numbers." \cite{MiddleSquare}
\end{itemize}
Notes:
\begin{itemize}
    \item Generally the value of the seed has to be even, but can be padded with leading zeros.
    \item If the middle n digits are all zeroes, the generator then outputs zeroes indefinitely. If the first half of a number in the sequence is zeroes, the subsequent numbers eventually converges to zero.
\end{itemize}

\noindent\textbf{Linear Congruential}:
\begin{itemize}
    \item A linear congruential generator is a PRNG that represents an "additive  congruential  method", with foundations in improving upon "unsatisfactory" tests with entropy in fibonacci sequences. \cite{10.1145/321008.321019}
\end{itemize}
Notes:
\begin{itemize}
    \item The generator is not sensitive to the choice of c, 
as long as it is relatively prime to the modulus 
(e.g. if m is a power of 2, then c must be odd), 
so the value c=1 is commonly chosen.
    \item If c = 0, the generator is often called a multiplicative
congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c ≠ 0, the
method is called a mixed congruential generator.
    \item Parameters were chosen based on $2^32$ numbers in table 2 of the article "Tables of linear congruential generators of different sizes and good lattice structure." \cite{LEcuyer1999TablesOL}
\end{itemize}

\noindent\textbf{Lagged Fibonacci}:
\begin{itemize}
    \item The Lagged Fibonacci PRNG is a generalization of the Fibonacci Sequence \cite{lucas1891calcul}, where the sequence is generated based off a seed and the sum of the last two values is the PRN (which is also serves as the next seed).
\end{itemize}
Notes:
\begin{itemize}
    \item It is refered to a "lagged" generator, because "j" and "k" lag behind the generated pseudorandom value. 
    \item Our implementation is called a "two-tap" generator, in that you are using 2 values in the sequence 
to generate the pseudorandom number. However, note that a two-tap generator has some problems with 
randomness tests, such as the Birthday Spacings. Creating a "three-tap" generator could
addresses this problem.
\end{itemize}

\noindent\textbf{Park Miller}:
\begin{itemize}
    \item Park Miller (also known as Lehmer) can be viewed as a particular case of the Lemher PRNG, which is a particular case of the linear congruential PRNG, where c=0 and particular parameters are specified.
\end{itemize}
Notes:
\begin{itemize}
    \item "In 1988, Park and Miller \cite{10.1145/63039.63042}, suggested a Lehmer RNG with particular parameters m = 231 − 1 = 2,147,483,647 (a Mersenne prime M31) and a = 75 = 16,807 (a primitive root modulo M31), now known as MINSTD." \cite{ParkMiller}
\end{itemize}

\noindent\textbf{Mersenne Twister}:
\begin{itemize}
    \item "The Mersenne Twister algorithm is based on a matrix linear recurrence over a finite binary field" \cite{10.1145/146382.146383}
\end{itemize}
Notes:
\begin{itemize}
    \item This PRNG is similar to a common LFSR. Its MT19937 implementation is probably the most commonly used modern PRNG. 
    \item It is also the default generator in the Python language starting from version 2.3. 
    \item For our implementation, we used numpy's version of the Mersenne Twister.
\end{itemize}

@@

Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively. The stack of convolutional layers allow the network to discover complex patterns in the input." \cite{debernardi2018pseudo} Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus. Talk about the input xdata and ydata shape and reference the granular model Figure ~\ref{fig:Granular Experimental Model} for detail on how these data are aggregated.
